### some examples

Load the functions so we can call them
```{r}
source("roll_dnd_mobs.R")
```

Attack with 15 level 3 human ranger hunters with a shortsword.
```{r}
attack(24, +6, 1, 8, +4, AC = 15)
```

They can also attack with their off-hand using their bonus action, but for the damage we do not add the ability modifier.
```{r}
attack(24, +6, 1, 8, +0, AC = )
```

## monsters

the undead armies vs. dragon
```{r}
attack(29, +4, 1, 6, +2, AC = 18)
```

de frost giants
```{r}
attack(6, +4, 3, 12, +4, AC = 17)
```

Our hunters are colossus slayers, so they deal an extra 1d8 damage if the target's HP is below it's max HP: (only once per turn, only for first attack).
```{r}
attack(15, +6, 2, 8, +4, AC = 15)
```

Define a special case for our hunter's combined attack (you can too!)
```{r}
hunters <- function(n = 20, AC, advantage = FALSE, disadvantage = FALSE) {
  first <- attack(n, +6, 2, 8, +4, AC = AC, advantage = advantage, disadvantage = disadvantage)
  second <- attack(n, +6, 1, 8, +0, AC = AC, advantage = advantage, disadvantage = disadvantage)
  list(colossus = first, off_hand = second, sum = first$tot + second$tot)
}
```

Attack with 19 archers that have a +8 bonus to hit. They are also colossus slayers so they roll 2d8+4 damage against an AC of 15, with advantage.
```{r}
attack(n_mobs = 20, to_hit = +8, dmg_die_n = 2, dmg_die = 8, dmg_bonus = +4, AC = 15)
```

Do a stealth check for 15 human ranger hunters, who have +6 on stealth.
```{r}
check(15, +6, DC = 14)
```

A saving throw is the same as a skill check.
```{r}
save(15, +6, DC = 14)
```
